% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\makeatletter
\newsavebox\pandoc@box
\newcommand*\pandocbounded[1]{% scales image to fit in text height/width
  \sbox\pandoc@box{#1}%
  \Gscale@div\@tempa{\textheight}{\dimexpr\ht\pandoc@box+\dp\pandoc@box\relax}%
  \Gscale@div\@tempb{\linewidth}{\wd\pandoc@box}%
  \ifdim\@tempb\p@<\@tempa\p@\let\@tempa\@tempb\fi% select the smaller of both
  \ifdim\@tempa\p@<\p@\scalebox{\@tempa}{\usebox\pandoc@box}%
  \else\usebox{\pandoc@box}%
  \fi%
}
% Set default figure placement to htbp
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Lab Members},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{Lab Members}
\author{}
\date{\vspace{-2.5em}29 June 2026}

\begin{document}
\maketitle

{
\setcounter{tocdepth}{5}
\tableofcontents
}
\section{Principal Investigator}\label{principal-investigator}

\subsubsection{Jonathan Nelson, Ph.D.}\label{jonathan-nelson-ph.d.}

Hello, my name is Dr.~Jonathan Nelson, and I am an Assistant Professor
in the Division of Nephrology \& Hypertension at the Keck School of
Medicine of USC. I completed my undergraduate studies in Biochemistry at
the University of Washington before earning my PhD in Molecular and
Medical Genetics at Oregon Health \& Science University. My research
focuses on vascular biology and the renin-angiotensin system,
particularly how it regulates the kidney microvasculature. I am
passionate about using translational research to better understand
kidney disease and improve outcomes for patients with vascular and renal
conditions.

\section{Current Members}\label{current-members}

\subsubsection{Nicky Kim}\label{nicky-kim}

\paragraph{Laboratory Technician II}\label{laboratory-technician-ii}

Hi! My name is Nicky Kim and I am working in the Division of Nephrology
\& Hypertension in the Department of Medicine at Keck School of Medicine
of USC. I graduated with a Bachelor of Arts in Neuroscience from Reed
College in 2023, and I am now currently a research laboratory technician
in Dr.~Susan Gurley and Dr.~Jonathan Nelson's labs, researching kidney
disease through understanding the functions and effects of specific
genes, as well as examining roles of outside factors such as PFAS, in
transgenic disease mouse models.

\subsubsection{Kevin Shih}\label{kevin-shih}

\paragraph{Laboratory Technician II}\label{laboratory-technician-ii-1}

Hello, my name is Kevin, and I work in the Division of Nephrology at the
Keck School of Medicine at USC in Dr.~Nelson's Laboratory. I received my
Bachelor's of Science in Molecular, Cellular, and Developmental Biology
and my Master's of Science in Physiological Sciences at the University
of California, Los Angeles.

\subsubsection{Ronald Vaca}\label{ronald-vaca}

\paragraph{Master's Student}\label{masters-student}

Ronald is working towards graduating with a Master's of Science in
Public Health from the University of Southern California. He is also the
manager of the USC Translational Pathology Core and Clinical
Immunohistochemistry Laboratories at the Keck School of Medicine. He
received his Bachelor of Science in Kinesiology and Exercise Science
from California State University, Fullerton.

\subsubsection{Arjun Lakshmanan}\label{arjun-lakshmanan}

\paragraph{Undergraduate Student}\label{undergraduate-student}

\subsubsection{Jeff Karnsomprot}\label{jeff-karnsomprot}

\paragraph{Undergraduate Student}\label{undergraduate-student-1}

\subsubsection{Deeshan Weeraratne}\label{deeshan-weeraratne}

\paragraph{Undergraduate Student}\label{undergraduate-student-2}

Hello! My name is Deshan Weeraratne and I am a fourth-year undergraduate
at USC majoring in Human Biology and minoring in Healthcare Studies. I
joined the Nelson Lab in August 2025, and am currently investigating how
angiotensin II affects genetic function in kidney cells.

\subsubsection{Paul Cho}\label{paul-cho}

\paragraph{Undergraduate Student}\label{undergraduate-student-3}

Hello, my name is Paul Cho, a third-year undergraduate student at the
University of Southern California majoring in Human Biology and minoring
in Cinematic Arts! I've been a part of Dr.~Nelson's Lab since August
2025. My research focuses on how and to what degree Angiotensin II
affects the transcriptional pattern of different kidney cells.

\subsubsection{Erik Siranosian}\label{erik-siranosian}

\paragraph{Bridging the Gaps Student}\label{bridging-the-gaps-student}

Hello! My name is Erik Siranosian, and I am a 4th-year undergraduate at
the University of California, Los Angeles (UCLA), majoring in
Psychobiology and minoring in Chicano and Chicana Studies. I am also
part of UCLA's Science Teacher Education Program (STEP), where I'm
getting my Master of Education (M.Ed) and will be a secondary science
teacher. I conduct research in Dr.~Nelson's lab where I use R to analyze
kidney gene expression data to develop a reproducible spatial
transcriptomics workflow for identifying kidney cell types while
preserving their location within tissue. This work can be used for
further kidney research, hopefully improving downstream patient
outcomes. In the future, I hope to become a physician-scientist who
combines clinical practice, research, and education to improve care for
patients from underserved communities.

\subsubsection{Omid Sajjadi}\label{omid-sajjadi}

\paragraph{Master's Student}\label{masters-student-1}

Omid graduated from the University of Southern California with his
Master's of Science in Stem Cell Biology and Regenerative Medicine.

\subsubsection{Sam de Leve}\label{sam-de-leve}

\paragraph{Resource Employee}\label{resource-employee}

\section{Alumnus Members}\label{alumnus-members}

\subsubsection{Sienna Blanche}\label{sienna-blanche}

\paragraph{Master's Student}\label{masters-student-2}

Hello, my name is Sienna Blanche, and I am a Master's student at the
University of Southern California studying Global Medicine. I graduated
from the University of Southern California in 2025 with a Bachelor of
Science in Human Biology and a minor in Gender and Sexuality Studies.I
work as a research assistant in Dr.~Nelson's lab where I analyze kidney
gene expression using single-nucleus RNA sequencing. In the future, I
aspire to become a physician dedicated to advancing women's health and
global health equity by integrating clinical practice with research to
improve patient outcomes.

Sienna has since graduated with a Master's of Science from the
University of Southern California and now works as a Clinical Research
Associate as she applies to medical school.

\subsubsection{Victoria Quon-Chow}\label{victoria-quon-chow}

\paragraph{Laboratory Technician}\label{laboratory-technician}

Hello! My name is Victoria Quon-Chow, and I am a research technician in
Dr.~Nelson's lab. My research work focuses on the associations between
per- and polyfluoroalkyl substances (PFAS), diabetes, and renal
diseases. I graduated from the University of Southern California in 2024
with a Bachelor of Science in Human Biology and a minor in Nutrition and
Health Promotion. I am currently applying to medical school and aspire
to serve diverse populations while providing compassionate,
patient-centered care.

Victoria was accepted into the Kansas City University College of
Osteopathic Medicine and will begin her training in 2026.
Congratulations!

\subsubsection{Roman Thomas}\label{roman-thomas}

\paragraph{Bridging the Gaps Student}\label{bridging-the-gaps-student-1}

Hi! My name is Roman Thomas, and I am a fourth-year undergraduate
student at Vanderbilt University, double majoring in Biochemistry and
Medicine, Health \& Society on the premed track. I am currently
conducting research in Dr.~Jonathan Nelson's lab, where we are
developing a manuscript that provides insights into a standardized
method for identifying kidney cell types using single nucleus RNA
sequencing analysis in R. I plan to apply these skills in my
Neuropharmacology lab, where we investigate the effects of the M5
Muscarinic Acetylcholine Receptor on drug-seeking behaviors in mice. My
long-term goal is to become a plastic surgeon while working to address
healthcare disparities and ensure that my patients, especially from
historically underserved groups, receive the autonomy and care that has
often been denied to them in the past.

Roman is graduating from Vanderbilt with his Bachelor's of Arts in 2026.
Congratulations!

\subsubsection{Deborah Sohn}\label{deborah-sohn}

\paragraph{Undergraduate Student}\label{undergraduate-student-4}

Deborah is a 3rd year student at the University of Southern California.

\end{document}
